\documentclass[fontsize=11pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage[svgnames]{xcolor}
\usepackage[margin=0.75in]{geometry}
\usepackage{url}
\usepackage{textcomp}
\usepackage{hyperref}

\makeatletter
\def\url@modernstyle{
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{}}}
\makeatother
\urlstyle{modern}

\frenchspacing
\pagestyle{empty}

\renewcommand{\familydefault}{\sfdefault}

\usepackage{sectsty}
\sectionfont{
  \usefont{OT1}{phv}{b}{n}
  \sectionrule{0pt}{0pt}{-5pt}{3pt}}

\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}
\newcommand{\sepspace}{\vspace*{1em}}

\newcommand{\MyName}[1]{
    \Huge \usefont{OT1}{phv}{b}{n} \hfill #1
    \par \normalsize \normalfont}

\newcommand{\MySlogan}[1]{
    \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1}
    \par \normalsize \normalfont}

\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
    \noindent\hangindent=2em\hangafter=0
    \parbox{\spacebox}{\textit{#1}}
    \hspace{1.5em} #2 \par}

\newcommand{\SkillsEntry}[2]{
    \noindent\hangindent=2em\hangafter=0
    \parbox{\spacebox}{\textit{#1}}
    \hspace{1.5em} #2 \par}

\newcommand{\AwardsEntry}[2]{
    \noindent\hangindent=2em\hangafter=0
    \parbox{\spacebox}{\textit{#1}}
    \hspace{1.5em} #2 \par}

\newcommand{\EducationEntry}[4]{
    \noindent \textbf{#1} \hfill
    \colorbox{Black}{\parbox{8.5em}{\hfill\color{White}#2}} \par
    \noindent \textit{#3} \par
    \noindent\hangindent=2em\hangafter=0 \small #4
    \normalsize \par}

\newcommand{\WorkEntry}[4]{
    \noindent \textbf{#1} \hfill
    \colorbox{Black}{\parbox{9em}{\hfill\color{White}#2}} \par
    \noindent \textit{#3} \par
    \noindent\hangindent=2em\hangafter=0 \small #4
    \normalsize \par}

\newcommand{\ProjectEntry}[4]{
    \noindent \textbf{#1} \noindent \textit{#3} \hfill {#2} \par
    \noindent \small #4
    \normalsize \par}

\newcommand{\AwardEntry}[4]{
    \noindent \textbf{#1} \noindent \textit{#3} \hfill {#2} \par
    \noindent \small #4
    \normalsize \par}

\newcommand{\AboutEntry}[1]{
    \noindent #1 \par}

\begin{document}

\MyName{Aryasomayajula Ram Bharadwaj}
\bigskip

{\small \hfill ram.bharadwaj.arya@gmail.com | 9108832338 | Bengaluru, India | github.com/rokosbasilisk}

\NewPart{ABOUT}
\AboutEntry{Backend Developer fluent in multiple languages, with a knack for refactoring legacy codebases and strong DevOps knowledge.}
\AboutEntry{ML Engineer with strong foundations in deep learning and skilled in implementing various neural network architectures.}

\NewPart{EDUCATION}
\EducationEntry
{B.Tech Electronics and Communications}
{2015 - 2019}
{GMR Institute of Technology, Andhra Pradesh}

\NewPart{WORK EXPERIENCE}

\WorkEntry
{Senior Developer at Innovation \& Development Labs}
{2019 - Present}
{Musigma Business Solutions, Bengaluru}
{%
\begin{itemize}
    \item Designed and implemented the entire backend stack for a semi-autonomous LLM Agent platform for data-analysis.
    \item Implemented strategies for automatically optimizing LLM agent's prompts based on user conversation feedback.
    \item Implemented support for retrieval-augmented generation (RAG) for LLM agents.
    \item Maintained an internal fork of Microsoft's Autogen framework with customized changes to display timestamps for each agent interaction and the capability to retrieve SQL databases.
    \item Performed evaluation of various hyperparameter optimization algorithms for time series models.
    \item Designed and built an automated intra-day trading system, and also acted as a team lead.
    \item Migrated legacy code for trade-signal generation from R to Scala.
    \item Implemented automatic hyperparameter search strategies to tune parameters for time series models based on previous performance on live market data.
    \item Designed and implemented a framework for deployment strategies (blue-green, canary) for ML models deployed on Kubernetes.
\end{itemize}}

\sepspace
\WorkEntry
{ML Alignment Theory Research Trainee}
{May 2023 - July 2023}
{Stanford Existential Risk Initiative, Remote}
{%
\begin{itemize}
    \item Underwent training for research in AI alignment and Agency foundations under guidance of John Wentworth.
\end{itemize}}

\NewPart{Skills}
\SkillsEntry{Languages}{Scala, Python, Java, R}
\SkillsEntry{ML}{Pytorch, JAX}
\SkillsEntry{DevOps}{Kubernetes, Docker-swarm}
\SkillsEntry{Misc}{Akka, Spring-boot}
\SkillsEntry{AI/ML}{LLM Fine-tuning, Adept in implementing most neural network architectures}

\NewPart{Projects}

\ProjectEntry{LLM Agent platform (Team Lead/ML Engineer/Backend Developer)}{}{}%
{An LLM Agent orchestrator platform, for automating data science tasks. Deployed into production for internal use for two major clients.}
\sepspace
\newpage
\ProjectEntry{\href{https://tplusone.org}{High Velocity Trading Platform} (Team Lead/Backend Developer/DevOps)}{}{}%
{A web-based application for advanced financial market analysis, executing and visualizing algorithmic trading strategies in real-time.}
\sepspace
\ProjectEntry{Next-Gen Model Operationalization platform (Backend Developer)}{}{}%
{An end-to-end web platform for operationalizing machine learning models. Provides a Jupyter notebook-like one-stop solution for deploying and monitoring ML models.}
\sepspace
\ProjectEntry{\href{https://github.com/rokosbasilisk/code-eval-harness}{Opensource Contributions}}{}{}%
{\begin{itemize}
    \item Implemented a framework for evaluating code generated by language models in a sandboxed environment, including the evaluation of language models' performance in math-word problems.
    \item Built a platform for generating debate transcripts given a set of topics using GPT-4. Benchmarked Mistral and Pythia models by LoRA fine-tuning them on these debate transcripts. \href{https://github.com/rokosbasilisk/synthetic_debates/}{(link)}
\end{itemize}}

\NewPart{Awards}

\AwardEntry{AI Alignment Awards}{www.alignmentawards.com}{July 2023}{My research proposal was one of the winning entries for the "goal misgeneralization" track.}
\sepspace
\AwardEntry{Honorable Mention}{Alignment Research Center}{Mar 2022}{ELK (Eliciting Latent Knowledge) is an open theoretical research problem in AI safety/AI alignment. ARC hosted a competition for promising proposals.}
\sepspace
\AwardEntry{Impact Award}{Musigma Business Solutions}{October 2022, December 2023}{Recognized for self-engagement with challenges, DevOps and integration skills, and designing the entire LLM-Agent conversation platform.}
\sepspace
\AwardEntry{Star Performer of the Team}{Musigma Business Solutions}{2019 to 2023}{Received the SPOT award six times for exceptional contributions.}
\sepspace
\AwardEntry{Bronze Position}{Build-on-Redis Hackathon}{Feb 2021}{Built a natural-language semantic code-search using codeBERT's embeddings for the Build-on-Redis hackathon organized by Redis-conf.}

\end{document}

