\documentclass[fontsize=11pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage[svgnames]{xcolor}
\usepackage[margin=0.75in]{geometry}
\usepackage{url}
\usepackage{textcomp}
\usepackage{hyperref}

\makeatletter
\def\url@modernstyle{
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{}}}
\makeatother
\urlstyle{modern}

\frenchspacing
\pagestyle{empty}

\renewcommand{\familydefault}{\sfdefault}

\usepackage{sectsty}
\sectionfont{
  \usefont{OT1}{phv}{b}{n}
  \sectionrule{0pt}{0pt}{-5pt}{3pt}}

\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}
\newcommand{\sepspace}{\vspace*{1em}}

\newcommand{\MyName}[1]{
    \Huge \usefont{OT1}{phv}{b}{n} \hfill #1
    \par \normalsize \normalfont}

\newcommand{\MySlogan}[1]{
    \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1}
    \par \normalsize \normalfont}

\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
    \noindent\hangindent=2em\hangafter=0
    \parbox{\spacebox}{\textit{#1}}
    \hspace{1.5em} #2 \par}

\newcommand{\SkillsEntry}[2]{
    \noindent\hangindent=2em\hangafter=0
    \parbox{\spacebox}{\textit{#1}}
    \hspace{1.5em} #2 \par}

\newcommand{\EducationEntry}[4]{
    \noindent \textbf{#1} \hfill
    \colorbox{Black}{\parbox{8.5em}{\hfill\color{White}#2}} \par
    \noindent \textit{#3} \par
    \noindent\hangindent=2em\hangafter=0 \small #4
    \normalsize \par}

\newcommand{\WorkEntry}[4]{
    \noindent \textbf{#1} \hfill
    \colorbox{Black}{\parbox{9em}{\hfill\color{White}#2}} \par
    \noindent \textit{#3} \par
    \noindent\hangindent=2em\hangafter=0 \small #4
    \normalsize \par}

\newcommand{\ProjectEntry}[4]{
    \noindent \textbf{#1} \hfill {#2} \par
    \noindent \textit{#3} \par
    \noindent \small #4
    \normalsize \par}

\newcommand{\AwardEntry}[4]{
    \noindent \textbf{#1} \hfill {#2} \par
    \noindent \textit{#3} \par
    \noindent \small #4
    \normalsize \par}

\newcommand{\AboutEntry}[1]{
    \noindent #1 \par}

\begin{document}

\MyName{Aryasomayajula Ram Bharadwaj}
\bigskip

{\small \hfill ram.bharadwaj.arya@gmail.com | 9108832338 | Bengaluru, India | github.com/rokosbasilisk}

\NewPart{ABOUT}
\AboutEntry{Versatile Backend Developer and ML Engineer with expertise in refactoring legacy codebases, implementing ML models, and strong DevOps knowledge. Skilled in multiple programming languages and passionate about AI alignment and safety.}

\NewPart{EDUCATION}
\EducationEntry
{B.Tech Electronics and Communications}
{2015 - 2019}
{GMR Institute of Technology, Andhra Pradesh}

\NewPart{PROFESSIONAL EXPERIENCE}

\WorkEntry
{Senior Developer at Innovation \& Development Labs}
{2019 - Present}
{Musigma Business Solutions, Bengaluru}
{%
\begin{itemize}
\item Led development of multiple high-impact projects in LLM Trading, automated trading, and ML operationalization.
\item Specialized in backend development, DevOps, and ML engineering across various domains.
\item Received multiple recognitions including Impact Awards and Star Performer of the Team.
\end{itemize}}

\sepspace

\WorkEntry
{ML Alignment Theory Research Trainee}
{May 2023 - July 2023}
{Stanford Existential Risk Initiative, Remote}
{%
\begin{itemize}
    \item Underwent training for research in AI alignment and Agency foundations under guidance of John Wentworth.
\end{itemize}}

\NewPart{KEY PROJECTS}

\ProjectEntry{LLM Agent Platform}{2022 - 2023}{Team Lead, ML Engineer, Backend Developer}
{%
\begin{itemize}
\item Designed and implemented a semi-autonomous data analysis platform powered by LLM Agents.
\item Developed automatic prompt optimization strategies and integrated Retrieval-Augmented Generation (RAG) support.
\item Maintained a customized fork of Microsoft's Autogen framework.
\item Successfully deployed for two major clients, assisted client teams in creating usecases.
\end{itemize}}

\sepspace

\ProjectEntry{\href{https://tplusone.org}{High Velocity Trading Platform}}{2020 - 2021}{Team Lead, Backend Developer, DevOps}
{%
\begin{itemize}
\item Refactored backend code and migrated deployment from bare-metal to Kubernetes.
\item Implemented automated hyperparameter search for ARIMA models.
\item Rewrote legacy trade-signal generation from R to Scala using Akka framework.
\item Enabled near real-time metric calculation and portfolio visualization.
\end{itemize}}

\sepspace

\ProjectEntry{Next-Gen Model Operationalization Platform}{2019 - 2020}{Backend Developer}
{%
\begin{itemize}
\item Developed automatic retraining pipelines for image classification models.
\item Designed and implemented Java microservices for creating and serving Jupyter notebooks.
\item Engineered a microservice for deploying ML models in a DAG structure with canary and blue-green deployment strategies.
\item Created dashboards for monitoring model and resource usage metrics.
\end{itemize}}

\sepspace

\ProjectEntry{\href{https://github.com/rokosbasilisk/code-eval-harness}{Open Source Contributions}}{Ongoing}{Individual Contributor}
{%
\begin{itemize}
\item Developed a framework for evaluating LLM-generated code in a sandboxed environment.
\item Conducted experiments to evaluate LLMs finetuned on debates, implemented mechanism for generating synthetic debate transcripts.
\item Benchmarked Mistral and Pythia models using LoRA fine-tuning on debate transcripts.
\end{itemize}}

\NewPart{SKILLS}
\SkillsEntry{Languages}{Scala, Python, Java, R}
\SkillsEntry{ML Frameworks}{PyTorch, JAX}
\SkillsEntry{DevOps}{Kubernetes, Docker-swarm}
\SkillsEntry{Frameworks}{Akka, Spring-boot}
\SkillsEntry{AI/ML}{LLM Fine-tuning, Neural Network Architecture Implementation}

\NewPart{AWARDS \& RECOGNITIONS}

\AwardEntry{AI Alignment Awards}{July 2023}{www.alignmentawards.com}
{Winning entry for the "goal misgeneralization" track research proposal.}

\sepspace

\AwardEntry{Honorable Mention}{Mar 2022}{Alignment Research Center}
{Recognition for proposal in the ELK (Eliciting Latent Knowledge) competition.}

\sepspace

\AwardEntry{Impact Award}{October 2022, December 2023}{Musigma Business Solutions}
{Recognized for self-engagement, DevOps skills, and designing the LLM-Agent conversation platform.}

\sepspace

\AwardEntry{Star Performer of the Team}{2019 to 2023}{Musigma Business Solutions}
{Received the SPOT award six times for exceptional contributions.}

\sepspace

\AwardEntry{Bronze Position}{Feb 2021}{Build-on-Redis Hackathon}
{Built a natural-language semantic code-search using codeBERT's embeddings.}

\end{document}
