\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{lmodern}

\pagenumbering{gobble}

\begin{document}

\begin{letter}{The Admissions Committee \\ University of Utah}
\opening{To the Admissions Committee:}

My name is \textbf{Suprit Kulkarni}, and I have over half a decade of experience working with machine learning-driven systems across financial and IoT domains. I supervised Ram Bharadwaj during our time at Mu Sigma's Innovation \& Development Labs, serving as his Team Lead for six months while designing an in-house MLOps platform.

Ram's contributions to the MLOps platform were exceptional. He conducted in-depth research on model operationalization, drawing insights from emerging research papers on model evaluation, safety, and explainability. Notably, his work extended beyond regular duties, including active contributions to opensource LLM Evaluation research framework back in 2020, demonstrating his commitment to AI Alignment \& Safety research.

What sets Ram apart is his self-driven approach to research. Despite a demanding work schedule, he consistently pursued advanced understanding in AI, particularly in areas of model interpretability and safety. His continued efforts to engage with cutting-edge AI research showcase a rare motivation and intellectual drive that distinguishes potential academic researchers.

Professionally, Ram is remarkably concise yet articulate. He defends his technical and philosophical opinions on AI design with remarkable precision, using minimal words but maximum impact. This characteristic, combined with his technical prowess, makes him an ideal candidate for rigorous academic research.

Having worked with numerous PhD and Masters graduates in Machine Learning, I confidently recommend Ram for the PhD program at the University of Utah. His skills as a backend developer and ML Engineer, coupled with his deep research interests, make him an exceptional candidate who would bring significant value to your program.

\closing{Sincerely,\\[4pt]
Suprit Kulkarni\\
Associate Technical Architect\\
Quantiphi}

\end{letter}

\end{document}
